A pipeline to analyse time-course gene expression data

### 2019-07-19 scripts/manuscript.Rmd
comments about installation

- Do we need installation instructions for moanin in this document, since its not on CRAN/bioconductor? Also, how its set up now (doing make file, which compiles the documentation, etc), probably prohibits use of, e.g. `install_github` from `devtools`. If able to call `install_github("NelleV/2019timecourse-rnaseq-pipeline", subdir="bin/moanin", dependencies=TRUE)` would be simpler (would also install the dependencies and get around problems in script)
- I got an error in installation of packages:

@@

- `biocLite` is no longer the recommended way to install bioconductor. Instead `BiocManager::install(c('edge', 'NMI'))`. But this is dependent on bioconductor/R version.

>>>>

- Do we need installation instructions for moanin in this document, since its not on CRAN/bioconductor? Also, how its set up now (doing make file, which compiles the documentation, etc), probably prohibits use of, e.g. `install_github` from `devtools`. If able to call `install_github("NelleV/2019timecourse-rnaseq-pipeline", subdir="bin/moanin", dependencies=TRUE)` would be simpler (would also install the dependencies and get around problems in script)
- I got an error in installation script for  packages:

@@

- `biocLite` is no longer the recommended way to install bioconductor. Instead `BiocManager::install(c('edge', 'NMI'))`. But this is dependent on bioconductor/R version. Also, now that docker, can you change the installation to just be simple one-liner (and `BiocManager::install` can also do non-bioc packages, and is much more reliable.)
